---
title: "p8105_hw5_sl5009"
author: "Shengzhi Luo"
date: "19/11/2021"
output: github_document
---


```{r,setup,include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1
```{r,message=FALSE}
homicide_df=
  read_csv("./data/homicide-data.csv",na=c("","Unknown")) %>% 
  mutate(
    city_state=str_c(city,state),
    resolution=case_when(
      disposition=="Closed without arrest" ~ "unsolved",
      disposition=="Open/No arrest" ~ "unsolved",
      disposition=="Closed by arrest" ~ "solved"
    )) %>% 
  relocate(city_state) %>% 
  filter(city_state!="TulsaAL")
```

Let's focus on Baltimore,MD.

```{r}
baltimore_df=
  homicide_df %>% 
  filter(city_state=="BaltimoreMD")
baltimore_summary=
  baltimore_df %>% 
  summarise(
    unsolved = sum(resolution=="unsolved"),
    n=n()
  )

baltimore_test=
  prop.test(
    x=baltimore_summary %>% pull(unsolved),
    n=baltimore_summary %>% pull(n)) 

baltimore_test %>% 
  broom::tidy() 
```
Let's try to iterate across cities!

First off, write a function and test it on a few sample cities.
```{r}
prop_test_function=function(city_df){
  city_summary=
    city_df %>% 
    summarise(
     unsolved = sum(resolution=="unsolved"),
     n=n()
  )

 city_test=
   prop.test(
    x=city_summary %>% pull(unsolved),
    n=city_summary %>% pull(n)) 
 
 return(city_test)
}

prop_test_function(baltimore_df)


homicide_df %>% 
  filter(city_state=="AlbuquerqueNM") %>% 
  prop_test_function()

```

Let's iterate across all cities.

```{r}
results_df=
  homicide_df %>% 
  nest(data=uid:resolution) %>% 
  mutate(
    test_results=map(data,prop_test_function),
    tidy_results=map(test_results,broom::tidy)
  ) %>% 
  select(city_state,tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state,estimate,starts_with("conf"))

```


Try to make a plot showing estimates and confidence intervals.


```{r}
results_df %>% 
  mutate(city_state=fct_reorder(city_state,estimate)) %>% 
  ggplot(aes(x=city_state,y=estimate))+
  geom_point()+
  geom_errorbar(aes(ymin=conf.low,ymax=conf.high))+
  theme(axis.text.x=element_text(angle=90,vjust = 0.5,hjust=1))
``` 

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarise(
    unsolved=sum(resolution=="unsolved"),
    n=n()
  ) %>% 
  mutate(
    test_results=map2(unsolved,n,prop.test),
    tidy_results=map(test_results,broom::tidy)
  ) %>% 
  select(city_state,tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state,estimate,starts_with("conf"))
```

## Problem 2

Start with a dataframe containing all file names.
```{r,message=FALSE}
file_df=
  tibble(file=list.files(path="./data/zip_data")) 
longitu_df=
  file_df %>% 
 mutate(
    data=purrr::map(file,~read_csv(file.path("./data/zip_data",.)))
  )
longitu_df
```

Tidy the result
```{r}
long_df=
  longitu_df %>% 
  mutate(
    control_arm=substr(file,1,3),
    subject_id=substr(file,5,6)
  ) %>% 
  relocate(control_arm,subject_id) %>% 
  select(-file) %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "value"
  ) %>% 
  mutate(
    week=as.numeric(week)
  )
long_df
```

Make a spaghetti plot showing observations on each subject over time.
```{r}
long_df %>% 
  ggplot(aes(x=week,y=value,color=subject_id))+
  geom_point()+
  geom_line()+
  facet_grid(.~control_arm)
```
As the plots above, the values of experimental arm group are generally higher than control arm group. The values of the control arm group change around the beginning point over time while the values in experimental group increased over time.

## Problem 3
Download the dataset
```{r}
library(tidyverse)
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write a function
```{r}
replace_function = function(vector){
    if(is.numeric(vector)){
      replace_value = mean(vector, na.rm=TRUE)
    }
  else if(is.character(vector)){
      replace_value = "virginica"
    }
  replace_na(vector,replace_value)
}
iris_df =
  iris_with_missing %>% 
  map_df(replace_function)
iris_df
```

